### 2017-04-17 paper/evaluation.tex
pass on RQ6

To answer this research question we selected projects as follows.  To
avoid noise in measuring flakiness we first discarded projects
containing failing tests.  Then, we sorted projects in descending
order of their execution times and selected the top ten projects from
the resulting set.  In this experiment, the baseline technique is
sequential execution (\ie{}, configuration \Seq{}) and the evaluation
techniques consist of all configuration modes listed in
Section~\ref{sec:modes}.  We ran each of those techniques for \Fix{X}
times computing elapsed time and number of failing tests in each run.
Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
results we obtained.

@@

>>>>

To answer this research question, we considered all six parallel
levels from Section~\ref{sec:modes} and we selected the top 10
projects with long-running tests suites that satisfies the following
criteria: (1) tests run in sequence by default and (2) test suite
consists only by passing tests. The first criteria is to use the
default execution (\ie, configuration \Seq{}) as a baseline to compare
speedup with the other parallel configurations. The second criteria is
to avoid introducing noise when measuring the rate of flakiness caused
by the non-deterministic execution of tests. We are interested only in
failures manifested when parallelism is enabled. Since the number of
failing tests may vary, we run each project three times and report
report the average elapsed time and rate of flakiness.
Figures~\ref{tab:rq6-efficiency} and~\ref{tab:rq6-flaky} summarize the
results obtained.

@@

\Fix{Elaborate results from flakiness}

\Fix{Conclude}
